### 2014-04-24 Response_to_R0_Reviews.tex

    [1] Zhai, Liang, et al. ``Correlation between SWEI and ARFI image findings
    in ex vivo human prostates.'' Ultrasonics Symposium (IUS), 2009 IEEE
    International. IEEE, 2009.

    [2] K.J Parker, S.R Huang, R.M Lerner et al. Elastic and ultrasonic
    properties of the prostate IEEE Ultrason Sympos Proc, 2 (1993), pp.
    1035–1038

    [3] A.E Worthington, J Trachtenberg, M.D Sherar, Ultrasound properties of
    human prostate tissue during heating, Ultrasound in Medicine \& Biology,
    Volume 28, Issue 10, October 2002, Pages 1311-1318.

    The following text has been added to Section III(C):

    \input{arfi_normalization}

@@

    \item \textit{pg 12, line 329, change ``compliment'' to ``complement''.}

    Thank you for catching this grammatical error.  It actually existed in both
    the abstract and conclusion sections, and it has been corrected in both
    sections.

    \item \textit{Note that in my version of the manuscript, the figures and
            the captions written below them are blurry and difficult to read.
            This may just be a formatting issue with the automatic reviewer
            support system, but it is worth confirming that figures and their
            captions will be clear for publication.}

    High resolution images were uploaded for the review process, but their
    quality was definitely degraded during the rendering of the review PDF.  We
    will make sure that all images are propoerly reproduced at full resolution
    in new PDFs that are rendered of this manuscript.

### 2014-04-24 arfi_methods.tex
more ARFI normalization info

Displacement estimation was performed using a phase-shift estimator on the
beamformed in-phase and quadrature (IQ) data~\cite{Loupas95,pinton06}. The ARFI
data were then normalized as a function of depth to account for attenuation and
focal gain effects.  This normalization was performed using a displacement
profile measured in a homogeneous tissue-mimicking phantom that was low-pass
filtered with a cutoff-frequency of 0.8 mm$^{-1}$.  This filtered normalization
profile was applied to all displacements in the entire data set at each time
step.

>>>>

Displacement estimation was performed using a phase-shift estimator on the
beamformed in-phase and quadrature (IQ) data~\cite{Loupas95,pinton06}.
\input{arfi_normalization}
